Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-04-24 eg6-letters/long-paper/prc-dvcshelium.tex
Update Fucini's results with authors comments

We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model compared to the 
data~\cite{Liuti:2005gi} is based on the hypothesis that the main nuclear effects are 
included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
appears that this model undershoots the results systematically. However, a new independent 
calculation \cite{Fucini:2018gso}, using similar principles but with a more recent nuclear spectral 
function, has been able to reproduce the data very well. Another factor in the difference is that the
recent calculation from Fucini {\it et al.}~\cite{Fucini:2018gso} benefited from using the precise 
kinematic of each points. This feature appears to have a significant impact on some points, for 
instance the $-t$ distribution appears to have a peculiar structure well reproduced by the 
calculation. For this reason, we provide the detailed kinematic of each result presented in
appendix \ref{sec:fullresults}.

@@

An interesting way to look into this data is to show the result on incoherent nuclear DVCS compared 
with the free proton one. We can for instance make a ratio, in a fashion similar to the EMC 
effect, which allows to cancel out
the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
in Fig. \ref{fig:IncRatios}.
Notably, the calculation from Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer to the
others, hinting that maybe the better results with the raw asymmetries was linked to the
input model they used for the free nucleon GPD. Also, they appear to somewhat reproduce the 
shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
Altogether, this result confirms that most models significantly overshoot the data and that 
the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \% compared to the free proton.

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, the calculation from Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the
	the black dot-dash line is the calculation from Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}

>>>>

We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model compared to the 
data~\cite{Liuti:2005gi} is based on the hypothesis that the main nuclear effects are 
included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
appears that this model undershoots the results systematically. However, a new independent 
calculation \cite{Fucini:2018gso}, using similar principles but with a non diagonal nuclear spectral 
function \cite{Viviani:2001wu} based on the Av18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
well. Another factor in the difference is that the recent calculation from Fucini {\it et 
al.}~\cite{Fucini:2018gso} benefited from using the precise kinematic of each points presented 
in appendix \ref{sec:fullresults}. Including this information appears to have a significant 
impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
which is well reproduced when using this information.

@@

An interesting way to look into this data is to show the result on incoherent nuclear DVCS compared 
with the free proton one. We can for instance make a ratio, in a fashion similar to the EMC 
effect, which allows to cancel out
the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
in Fig. \ref{fig:IncRatios}.
Notably, the calculation from Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer to the
other with this observable, hinting that maybe the different results with the raw asymmetries 
was linked to the input model they used for the free nucleon GPD rather than the nuclear model. 
Also, they appear to reproduce the 
shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
Altogether, this result confirms that most models significantly overshoot the data and that 
the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \% compared to the free proton.

@@

\begin{figure}[tbp!]
\center
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
	represented with black squares and the HERMES 
	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, a calculation adapted from Fucini 
	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the
	the black dot-dash line is the calculation from Guzey {\it et al.}~\cite{Guzey:2008th}.}
\label{fig:IncRatios}
\end{figure}
